\documentclass[a4paper]{article}
\usepackage[margin=1cm]{geometry}
\usepackage[utf8]{inputenc}
\usepackage{amsfonts,amssymb,amsmath}
\pagestyle{empty}
\begin{document}
calculus of communicating systems

processes which have changing structure

communication may carry information which change the linkage

Petri nets, CSP, ACP, CCS are not expressive enough

Hewitt's Actors model lacks some mathematical analysis

$\pi$-calculus : processes pass references to other processes

recent attempts to combine $\lambda$-calculus and process calculi

Engberg and Nielsen extensions to CCS

Example 1: Agent $P$ sends value 5 to agent $R$ on link $a$.

$P=\bar a5.P^\prime$

$R=a(x).R^\prime$

Whole system is $(\bar a5.P^\prime|a(x).R^\prime)\setminus a$

$\setminus a$ is a restriction and indicates that $a$ is private to $P$ and $R$.

Exemple 2: $P$ is connected to $Q$ by a link $b$. It sends both the link $a$ and the value 5 to $Q$. $Q$ receives a link and a value on $b$, and transmit the value along that link. $P$ is initially linked to $R$ with link $a$, but sends that link to $Q$.

This is denoted $(\bar ba.\bar b5.P^\prime|b(y).b(z).\bar yz.0|a(x).R^\prime)\setminus a\setminus b$

This becomes $(P^\prime|\bar a5.0|a(x).R^\prime)\setminus a\setminus b$.

Graphically, the system transitions from a $P$ connected through $b$ to $Q$ and through $a$ to $R$ to a $P^\prime$ connected through $b$ to $Q^\prime$ itself connecte to $R$ through $a$.

Collapse of links, variables, and data into the same type of entity.

$\pi$-calculus deals only with names and agents.

Two CCS operators : restriction and input-prefix.

Restrictoin and input-prefix are both name-binding operators.

Restriction localises the scope of a name.

Input-prefix is similar to abstractoin in the $\lambda$-calculus.

New syntax : $(x)P$ means $P\setminus x$.

Example 2 becomes $(a)(b)(\bar b a.\bar b 5.P^\prime|b(y).b(z).\bar y z.0|a(x).R^\prime)$.

The purpose of communication is to transmit and receive names.

The $\lambda$-calculus aims for universality for functional computation.

The $\pi$-calculus aims for universality for concurrent computation.

Content of paper : examples + important algebraic properties.

Semantics of $\pi$-calculus to be found in another paper.

Equational theory of bisimilarity.

Bisimilarity is preserved by instantiation of names.

The equational theory of weak equality is a direct generalization of the from CCS.

\hrule

\textbf{Section 2}

Names and agents.
Agents are particular processes.
Agents have an arity.

Summation of agents: behavior is one of the behavior defined in the summation.

$\bar y x.P$, $y(x).P$, $\tau.P$ : prefix form

$\bar y x$ is a negative prefix, and may be thought of as an output port

$\bar y x.P$ outputs the name $x$ at port $\bar y$ and then behaves like $P$

$y(x)$ is a positive prefix, and may be thought as an input port

$y(x).P$ inputs an arbitrary name at port $y$ and then behaves like $P$, in which $x$ has been substituted with the supplied name.

$P_1|P_2$ : composition of processes acting in parallel

$(x)P$ : restriction : ports $x$ and $\bar x$ are hidden

$[x=y]P$ : behave like P only if $x$ and $y$ are identical

$A(y_1,\dots,y_n)$: Agent which must have a definining equation given somewhere.

Matching is not necessary but adds expressive power.

Free names, $\alpha$-conversion equivalence, vectors of names, notations for substitutions.

In prefixes, left is the subject and right is the object or parameter

Precedence rules.

Summation is last ; composition is before ; restriction/prefix/match are first

Differences from $\lambda$-calculus : parallelism ; names cannot be instantiated to agents

Synchronization of the negative and positive prefixes.

If multiple agents have the same name free, this represents shared knowledge.

A CCS sort contains both names and co-names.

The free names of an agent can grow, because agents can receive new names.

The semantics of $\pi$-calculus is presented as a labelled transition system with structural inference rules, with strong bisimulatoin and strong equivalence which corresponds to strong semantic equality.

\hrule
\textbf{Section 3}

$\bar x.P^\prime|y(z).Q^\prime|R\to^{\tau}P^\prime|Q^\prime\{x/z\}|R$

$(y)(\bar yx.P^\prime|y(z).Q^\prime)|R\to^{\tau}(y)(P^\prime|Q^\prime\{x/z\})|R$

Provable equation:

$(y)(\bar yx.P^\prime|y(z).Q^\prime)=\tau.(y)(P^\prime|Q^\prime\{x/z\})$

Scope intrusion requires renaming free variables through $\alpha$-conversion.

Process that takes a parameter by reference : Agent passes a private link to another agent.

$(x)(\bar yx.P^\prime|R)|y(z).Q^\prime\to^{\tau}(x)(P^\prime|R|Q^\prime\{x/z\})$

The scope of the restriction must be extended to include both P and Q.

Two transmit two names to either one or the other of the agent requires an indirection with another process which will have a task to perform the delivery.

This idea is the basis for the encoding of data structures as processes.


\end{document}
